### 2018-07-18 experiments.tex
more on mutants

We ran 2,350 mutants of pyfakefs.  Using the failure determinism check
in 60 second test runs let us kill 98 mutants that were not killed
during 60 seconds of testing without a reference or the failure
determinism check, using the same seed.  Of these, 71 could not even be killed by 120
seconds of testing using complete differential testing with Mac OS X
as a reference.  In contrast, the kill rate for the entire set of
mutants not killed without a reference, using 120 seconds of
differential testing was...

>>>>

We ran 2,350 mutants of pyfakefs.  Using the failure determinism check
in 60 second test runs let us kill 98 mutants that were not killed
during 60 seconds of testing without a reference or the failure
determinism check, using the same seed.  Of these, 71 could not even be killed by 120
seconds of testing using complete differential testing with Mac OS X
as a reference, a kill rate of only 27.6\%.  In contrast, the kill rate for the entire set of 1478
mutants not killed when not using a reference, using 120 seconds of
differential testing was...
